---
title: Introduction
output: html_document
---

## Overview

*VERSO* is an algorithmic framework that processes variants profiles from viral samples to produce phylogenetic models of viral evolution. 
The approach solves a Boolean Matrix Factorization problem with phylogenetic constraints, by maximizing a log-likelihood function. 

```{r include=FALSE}
library(knitr)
opts_chunk$set(
concordance = TRUE,
background = "#f3f3ff"
)
```

## Installing VERSO

The R version of *VERSO* can be installed from Github. To do so, we need to install the R packages *VERSO* depends on and the devtools package. 


```{r eval=FALSE}
# install VERSO dependencies
if (!require("ape")) install.packages("ape")
if (!require("Rfast")) install.packages("Rfast")

# install VERSO library
if (!require("devtools")) install.packages("devtools")
library("devtools")
install_github("BIMIB-DISCo/VERSO", ref = "master")

# load VERSO library
library("VERSO")
```

## Debug

Please feel free to contact us if you have problems running our tool at daniele.ramazzotti1@gmail.com or d.maspero@campus.unimib.it. 
